\huge Modeling Intervention Strategies for United States TB Control

### 2013-07-29 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
added summary block to third column

    \begin{column}{.3\textwidth}
      %\vspace{-.5em}
      \begin{block}{An Agent-Based Implementation}
        Agent-based models capture disease dynamics on the individual level and
        reflect stochasticity and granularity lost in compartmental models.
        Agent-based counterparts to the Hill model were implemented in Netlogo
        and \texttt{C++}.
        \begin{columns}
          %\vspace{-2em}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{NLHMinc}
              \end{center}
              \caption{Incidence/million for R and NetLogo models (12 runs, $\Delta t$ = 0.1, popConst = 100)}
              \label{fig:NLHMinc}
            \end{figure}
          \end{column}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{finalRunSmall2}
              \end{center}
              \caption{Incidence/million for R and C++ models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}
              \label{fig:finalRun}
            \end{figure}
          \end{column}
        \end{columns}
      \end{block}

      \begin{block}{Stochastic Models as a Measure of Variability}
        \begin{columns}
          %\vspace{-2em}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN0dist}
              \end{center}
              \caption{USB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.016534$)}
              \label{fig:IN0dist}
            \end{figure}
          \end{column}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN1dist}
              \end{center}
              \caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
              \label{fig:IN1dist}
            \end{figure}
          \end{column}
        \end{columns}
      \end{block}

      \vspace{.9em}
      \begin{block}{References \& Acknowledgments}
        This research was supported via an NSF REU grant. 
        \small{[1] Hill, A. N., Becerra, J. E., \& Castro, K. G. (2012). Modelling
          tuberculosis trends in the USA. Epidemiology and infection, 140(10),
          1862.}
      \end{block}

>>>>

    \begin{column}{.3\textwidth}
      %\vspace{-.5em}
      \begin{block}{An Agent-Based Implementation}
        Agent-based models capture disease dynamics on the individual level and
        reflect stochasticity and granularity lost in compartmental models.
        Agent-based counterparts to the Hill model were implemented in Netlogo
        and \texttt{C++}.
        \begin{columns}[T]
          \vspace{-2em}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[height=0.8\textwidth,width=\textwidth]{NLHMinc}
              \end{center}
              \caption{Incidence/million for R and NetLogo models (12 runs, $\Delta t$ = 0.1, popConst = 100)}
              \label{fig:NLHMinc}
            \end{figure}
          \end{column}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[height=0.8\textwidth,width=\textwidth]{finalRunSmall2}
              \end{center}
              \caption{Incidence/million for R and C++ models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}
              \label{fig:finalRun}
            \end{figure}
          \end{column}
        \end{columns}
      \end{block}

      \begin{block}{Stochastic Models as a Measure of Variability}
        %\vspace{-0.5em}
        %\begin{columns}[T]
          %\begin{column}{.45\textwidth}
            %\begin{figure}[h]
              %\begin{center}
                %\includegraphics[height=0.5\textwidth,width=\textwidth]{IN0dist}
              %\end{center}
              %\caption{USB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.016534$)}
              %\label{fig:IN0dist}
            %\end{figure}
          %\end{column}
          %\begin{column}{.45\textwidth}
            %\begin{figure}[h]
              %\begin{center}
                %\includegraphics[height=0.5\textwidth,width=\textwidth]{IN1dist}
              %\end{center}
              %\caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
              %\label{fig:IN1dist}
            %\end{figure}
          %\end{column}
        %\end{columns}
        \begin{figure}[h]
          \begin{center}
            \includegraphics[height=0.25\textwidth,width=0.45\textwidth]{IN0dist}
            \includegraphics[height=0.25\textwidth,width=0.45\textwidth]{IN1dist}
          \end{center}
          \caption{USB and FB Incidence (\texttt{c++}) with fitted Normal curves (USB: $\mu = 0.233, \sigma = 0.016534$, FB: $\mu = 98.6, \sigma = 0.525294$)}
          \label{fig:INdist}
        \end{figure}
              %\caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
              %\label{fig:IN1dist}
      \end{block}

      \begin{block}{Summary}
        \begin{itemize}
          \item TB elimination is possible
          \item new framework for disease modeling
          \item something else
        \end{itemize}
      \end{block}
      %\vspace{.9em}
      \begin{block}{References \& Acknowledgments}
        This research was supported via an NSF REU grant. 
        \small{[1] Hill, A. N., Becerra, J. E., \& Castro, K. G. (2012). Modelling
          tuberculosis trends in the USA. Epidemiology and infection, 140(10),
          1862.}
      \end{block}
